Compositional Equivalences Based on Open pNets

### 2022-10-19 2016-Weak-FH-Bisim/WeakBisim.tex
resolution pbme doublons refs

This approach also allows us to specify a sufficient condition on allowed transitions to make weak bisimilarity compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
This is loosely related to works on the syntactic conditions on SOS rules to check whether weak bisimulation is a congruence for some process algebra operators \cite{GrootVaandrager1992}. Our approach is semantical and more global: our sufficient condition applies to all the synchronisations at a given composition level of an (open) system and not on individual rules. It is expressed on the open automaton (see Definition \ref{def:non-obspNet}).
%\TODO{Eric: relations with SOS rule formats?}

>>>>

This approach also allows us to specify a sufficient condition on allowed transitions to make weak bisimilarity compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
This is loosely related to works on the syntactic conditions on SOS rules to check whether weak bisimulation is a congruence for some process algebra operators \cite{GROOTE1992202}. Our approach is semantical and more global: our sufficient condition applies to all the synchronisations at a given composition level of an (open) system and not on individual rules. It is expressed on the open automaton (see Definition \ref{def:non-obspNet}).
%\TODO{Eric: relations with SOS rule formats?}
